Malacology: A Programmable Storage System Built on Ceph

### 2016-05-08 paper/paper.tex
deleted:    out/main.pdf 	modified:   paper.tex 	More changes in the intro

To illustrate the benefits and challenges of this approach we examine
the programmability of Ceph \autocite{weil_ceph_2006}, the increasingly
popular, production-level open-source distributed storage system.
Something of a storage swiss army knife, Ceph supports file, block, and
object interfaces simultaneously in a single cluster. By introducing
programmability concepts into Ceph, we can build new services by
carefully exposing internal storage services to applications.

@@

For example, Ceph \autocite{weil_ceph_2006} contains a cluster of
monitoring nodes (MONs) that use PAXOS to maintain a consistent view of
system-wide metadata such as data distribution parameters and cluster
membership. The RADOS object storage system is a cluster of storage
devices (OSDs) that provide Ceph with data durability and integrity
using replication, erasure-coding, and scrubbing
\autocite{weil_rados_2007}. The data distrubiton metadata maintained by
the cluster monitors is used by RADOS servers and clients to provide
consistent reads and writes, and both RADOS and the monitoring services
are used by a cluster of file system metadata servers that provide POSIX
semantics using sophisticated indexing and distributed locking services.
We contend that re-using and re-purposing these code-hardened subsystems
is paramount to successfully adapting storage systems to new APIs and
new storage devices without losing the benefits from years of
code-hardening work.

To illustrate the benefits and challenges of this approach we have
designed and evaluated Malacology, a programmable storage system for
constructing new functionality by re-purposing existing subsystem
abstractions contained in Ceph. We build the framework on Ceph by
leveraging a broad spectrum of existing services, including distributed
locking and caching services provides by MDSs, durability and logical
storage devices provides by RADOS, and propogation of consistent cluster
state provided by the monitoring service. As shown in Figure
\ref{fig:overview}, this framework is expressive enough to provide the
functionality necessary for implementing new services. Our contributions
are:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  a programmable storage system implementation that re-uses and extends
  existing abstractions. It includes:

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    inode abstractions for sequencer services
  \item
    consensus abstractions for policy versioning
  \item
    storage objects for persisting policies
  \item
    interface classes for new logical storage/metadata devices
  \end{enumerate}
\item
  example systems that use this framework

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    shared log service based on CORFU \autocite{balakrishnan_corfu_2012}
  \item
    metadata load balancer based on Mantle
    \autocite{sevilla:sc15-mantle}
  \end{enumerate}
\end{itemize}

>>>>

To illustrate the benefits and challenges of this approach we examine
the programmability of Ceph \autocite{weil_ceph_2006}, the increasingly
popular, production-level open-source distributed storage system.
Something of a storage swiss army knife, Ceph supports file, block, and
object interfaces simultaneously in a single cluster. Ceph's Reliable Autonomous Distributed Object Storage (RADOS) system is a cluster of storage
devices (OSDs) that provide Ceph with data durability and integrity
using replication, erasure-coding, and scrubbing
\autocite{weil_rados_2007}. 
% By introducing
% programmability concepts into Ceph, we can build new services by
% carefully exposing internal storage services to applications.

@@

For example, a Ceph cluster contains a small number of
monitoring nodes (MONs) that use PAXOS to maintain a consistent view of
system-wide metadata such as data distribution parameters and cluster
membership. The data distribution metadata maintained by
the cluster monitors is used by RADOS servers and clients to provide
consistent reads and writes, and both RADOS and the monitoring services
are used by a cluster of file system metadata servers that provide POSIX
semantics using sophisticated indexing and distributed locking services.
We contend that re-using and re-purposing these code-hardened subsystems
is paramount to successfully adapting storage systems to new APIs and
new storage devices without losing the benefits from years of
code-hardening work.

To illustrate the benefits and challenges of this approach we have
designed and evaluated Malacology, a programmable storage system for
constructing new functionality by re-purposing existing subsystem
abstractions contained in Ceph. We build the framework on Ceph by
leveraging a broad spectrum of existing services, including distributed
locking and caching services provides by MDSs, durability and logical
storage devices provided by RADOS, and propogation of consistent cluster
state provided by the monitoring service (see \ref{fig:overview}). As we will show in this paper, this framework is expressive enough to provide the
functionality necessary for implementing new services. Our contributions
are:

\paragraph{}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item A programmable storage system implementation that re-uses and extends existing abstractions. It includes:

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Extending file system metadata by a new type of inode that together with Ceph's capability subsystem implements high-performance, non-durable access serialization
  \item
    Re-using Ceph's PAXOS-based consensus infrastructure for versioning of metadata service load-balancing policies
  \item
    Re-using storage objects for persisting policies
  \item
    Extending object interface classes for new logical storage/metadata devices
  \end{enumerate}
\item
  Two example implementations and evaluations for feasibility of services that use this framework

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    A high-performance distributed shared log service called Zlog which is based on CORFU~\autocite{balakrishnan_corfu_2012}
  \item
    A re-implementation of the programmable Mantle metadata load balancing service using Malacology~\autocite{sevilla:sc15-mantle}
  \item 
    An application of the Mantle metadata load balancing service to manage 
  \end{enumerate}
\end{itemize}
